\addcontentsline{toc}{chapter}{List of Publications}

\chapter*{List of Publications} \label{sec:intro:pubs}
As part of my PhD work the following work was published by me:
\begin{itemize}
  \item \textbf{Charalampos Rotsos}, Jurgen Van Gael, Andrew W. Moore, and Zoubin
        Ghahramani. 2010. Probabilistic graphical models for semi-supervised
        traffic classification. In Proceedings of the 6th International Wireless
        Communications and Mobile Computing Conference (IWCMC '10). ACM, New
        York, NY, USA, 752-757.
    
  \item Mortier, R., Ben Bedwell, Glover, K., Lodge, T., Rodden, T., Rotsos, C.,
    et al. (2011). Supporting novel home network management interfaces with
    openflow and NOX. Presented at the SIGCOMM '11: Proceedings of the ACM
    SIGCOMM 2011 conference,  ACM. doi:10.1145/2018436.2018523

  \item Richard Mortier, Ben Bedwell, Kevin Glover, Tom Lodge, Tom Rodden,
    \textbf{Charalampos Rotsos}, Andrew W. Moore, Alexandros Koliousis, and Joseph
        Sventek. 2011. DEMO: Supporting novel home network management interfaces with
        openflow and NOX. SIGCOMM Comput. Commun. Rev. 41, 4 (August 2011),
        464-465.

  \item Madhavapeddy, A., Mortier, R., Gazagnaire, T., Proust, R., Scott, D.,
        Singh, B., et al. (2011). Constructing a “Functional” Cloud (Mirage
        2011), 1–10.
 
  \item Mortier, R., Rodden, T., Lodge, T., McAuley, D., \textbf{Rotsos, C.},
        Moore, A.W., Koliousis, A., Sventek, J., "Control and understanding:
        Owning your home network," Communication Systems and Networks
        (COMSNETS), 2012 Fourth International Conference on , vol., no.,
        pp.1,10, 3-7 Jan. 2012
  
  \item \textbf{Charalampos Rotsos}, Nadi Sarrar, Steve Uhlig, Rob Sherwood,
        and Andrew W. Moore. 2012. OFLOPS: an open framework for openflow
        switch evaluation. In Proceedings of the 13th international
        conference on Passive and Active Measurement (PAM'12), Nina Taft and
        Fabio Ricciato (Eds.). Springer-Verlag, Berlin, Heidelberg, 85-95. 

  \item Chaudhry, A., Madhavapeddy, A., \textbf{Rotsos, C.}, Mortier,
        R., Aucinas, A., Crowcroft, J., et al. (2012). DEMO: Signposts:
        end-to-end networking in a world of middleboxes. Presented at
        the SIGCOMM '12: Proceedings of the ACM SIGCOMM 2012 conference
        on Applications, technologies, architectures, and protocols for
        computer communication,  ACM.

  \item \textbf{Rotsos, C.}, Mortier, R., Madhavapeddy, A., Singh, B., \& Moore,
        A. W. C.  I. 2. I. I. C. O. (n.d.). Cost, performance \& flexibility in
        OpenFlow: Pick three. Presented at the Communications (ICC), 2012 IEEE
        International Conference on, vol., no., pp.6601,6605, 10-15 June 2012

  \item Anil Madhavapeddy, Richard Mortier, \textbf{Charalampos Rotsos}, David Scott,
        Balraj Singh, Thomas Gazagnaire, Steven Smith, Steven Hand, and Jon
        Crowcroft. 2013. Unikernels: library operating systems for the cloud.
        SIGPLAN Not. 48, 4 (March 2013), 461-472. 
\end{itemize}


