\def\baselinestretch{1}
\chapter{Conclusions and Future Work} \label{sec:conclusions}

\def\baselinestretch{1.66}

This chapter concludes the dissertation by summarising the work it described,
and noting areas in which further work is required.

\section{Summary}

This dissertation has addressed issues of control plane performance scalability
using the SDN paradigm.  Chapter~\ref{s:introduction:introduction} began by
motivating the requirement to scale the functionality of existing network
protocols and technologies in order to support the design limitation which are
highlighted by increased adoption of networks.  We argued that control plane
performance is multi-dimensional (e.g.~resource control, management,
connectivity), which have variable importance for application and depend highly
on the deployment environment. We claimed that speciailized control plane
architectures can mitigate network bottlenecks, introduced by protocol design,
while ensuring backwards compatibility and high performance, by addressing the
requirement and opportunities of the deployed environment. 

Chapter~\ref{ch:background} then considered background and related work to the
problem of network control. We provided a bottom-up design discussion on
available network control mechanisms. We elaborated on the architecture of
current network devices and presented a generic design model of the integration
between the control and data plane in a single device in order to highlight the
physical limitations in  network performance. Furthermore, we reviewed
the current production-level network control protocols and mechanisms for the
data link and network layers and it was argued that their ability for responsive
flexible and user friendly control is reduced. Furthermore, we surveyed a
series of experimental approaches which address network control limitation and
provide flexible, distributed and evolvable control.  Namely we present Active
Network, Devolved Control of ATM Networks and Software Defined Networking. In
order to highlight the opportunities provided by these mechanisms, we concluded
this chapter with an extensive presentation of novel control applications build
on top of the SDN paradigm. 

The bulk of the experimental contribution of this dissertation was reported in
the following three chapters. Chapter~\ref{sec:sdn_scalability} analysed the
elementary scalability of the SDN paradigm. In this chapter, we presented two
measurement platforms, enabling network experimenters to evaluate the
performance of SDN architectures. \oflops is a high-precision
hardware-accelerated \of switch measurement platform which enables experimenters
to understand the performance behaviour of \of-enabled devices, and \sdnsim, a
lightweight high-precision network simulation and emulation framework. Using
\oflops, we develop and run a series of tests characterising the elementary
functionalities of the \of protocol and detect significant variance between
switch protocol implementations. \sdnsim is a high precision experimentation
environment, which allows users to implement their control logic and traffic
models and evaluate the performance of an SDN architecture. The platform
provides the ability to simulate, using the \ns{3} platform, or emulate, using
the Xen virtualisation platform, a experimental definition.  The platform
provides enhanced realism on the performance characteristics of the network
control plane, while through our evaluation we highlighted the scalability of
experimentation.  Using \sdnsim, we replicate the functionality of a small-scale
datacenter network and highlighted the effectiveness of control centralisation.

Chapter~\ref{sec:homework} elaborated the problem of management scalability in
modern home networks. Using ethnographic and measurement studies of the home
setting, we identified significant mismatches between the user-requirement and
user-understanding of network functionality and the existing technologies.
Motivated by this observation, we redesign the home router, implementing a
series of control modifications which enhance user control and bridge the user
perception with the underlying network functionality. The proposed architecture
is extended with a collaborative resource control mechanism which integrates
users application-level requirements with the ISP policy, in an effort to
develop a user-friendly control scheme for the last-mile bottleneck in
residential broadband networks. We presented the development of a strawman
implementation of our system and verified that the architectures incurs minimal
impact on network functionality, the protocol modifications remain
backwards compatible with a number of popular devices, OSes and applications and
that the resource control mechanism improves the support for latency and
bandwidth sensitive applications in congested residential networks. 

Chapter~\ref{sec:signpost} discussed Internet-scale naming and connectivity
scalability.  Through the work of this chapter, we aimed to develop a
decentralised and Internet-wide federated network between the devices of a user.
We motivated our effort by presenting the limitations of existing approaches in
terms of usability and privacy and argued that an evolved control plane for
end-hosts can address such limitations and support all required functionality.
We proposed the \signpost architecture providing secure, continuous and
decentralised inter-device connectivity. \signpost reuses existing connectivity
mechanisms to provide ad-hoc end-to-end path between devices. The system
provides a global naming structure and uses the DNS protocol to establish a
global control channel through which \signpost automates distributed evaluation
and configuration of connection establishing mechanisms.  We presented a
strawman implementation  of the \signpost architecture and its integration with
the \openvpn, TOR, SSH, Privoxy, NAT punching and DNS-SD mechanisms.  Using the
\signpost strawman implementation, we characterised the low impact of the
architecture to network functionality and its backwards compatibility with
existing applications. 

\section{Summary of Contributions}

The dissertation makes the following three contributions:

\paragraph{Control plane scalability} 
In this thesis we present the first scalability characterisation of \of
implementations. We highlighted the significant performance diversity between
implementations which can affect the performance and the correctness of control
architectures.  Furthermore, we developed \sdnsim, an experimentation platform
for SDN architectures, providing the ability to emulate and simulate network
experiments. \sdnsim provides high fidelity on replicating the control channel
of the network and provides intuitive control between fidelity and scalability. 
Using \sdnsim we evaluate the performance of a hierarchical control architecture
in a small-scale datacenter.

\paragraph{Management scalability}

This thesis presented a novel control architecture establishing scalable
management for home network. We presented a flow-based controller, which exploit
the social conventions in the home to manage introduction of devices  to the
network, and their subsequent access to each other and Internet hosted services.
Additionally, we proposed a modification in the control architecture of the ISP
network, which enables users to express and enforce their resource requirements
in a user-friendly manner. We provided strong evidence on the scalability,
backwards compatibility and effectiveness of our solution.  

\paragraph{Connectivity and naming scalability}

This thesis analysed the significant limitation introduced by the current
Internet architecture on the connectivity ability between the devices of users.
In order to mitigate these limitations we presented \signpost, a decentralised
control architecture providing global names for user devices and continuous
connectivity between them. We presented the flexibility of \signpost to
encapsulate a wide range of connection establishing mechanism and provided
strong evidence on its backward-compatibility with existing applications and its
performance scalability. 

\section{Future Work}
  
The experimental results and the practical solutions presented in the thesis
provide fruitful seeds to cultivate a wider research agenda on control plane
evolvability.

\subsection{Distributed network control}

One the first use cases of the SDN paradigm was the centralisation of control in
order to improve policy effectiveness and ease network management.  Nonetheless this
vision has evolved and refocuses on the development of distributed control
architectures. Control distribution is motivated by two observations.  Firstly,
load and latency of the control channel increases proportionally to the size of the
network, while reliability guarantees relax. Secondly,
defining one global control policy which is able to encapsulate multiple policy
aspects (e.g.~security, performance, access control) exhibits significant
complexity. Applications have shifted to a multi-controller paradigm using
either centralised proxies~\cite{flowvisor-osdi} or separating the network
in domains and use distribute algorithms to synchronise state between
controllers~\cite{Koponen10}. 

The work presented in Chapter~\ref{sec:sdn_scalability} provide a scalable
control experimentation platform, a powerful tool to understand further the
impact of  distributed design patterns on the performance of a network.
Hierarchical control, as presented through the evaluation experiment using the
\sdnsim, has low impact on network performance, but a complete architectural
design requires further evaluation of mechanisms with strong control plane
responsiveness and reliability guarantees. 

\subsection{User-centric networking}

As we have discussed in Chapter~\ref{sec:homework}, current network technologies
exhibit a significant mismatch with the user requirements. The outcomes from the
previous two chapter have provided strong evidence on the ability of networks to
reconsider control and augment it with meaningful user input. Rather than
relegating users to an artifact of the application layer, accommodating users
and their relationships at all layers of the system can improve user
satisfaction and network functionality. We consider two main extensions on the
work of the thesis, towards this goal. 

Firstly, a number of areas arise from the work in Chapter~\ref{sec:homework}.
The presented control architecture provides novel opportunities to augment home
network functionality and exploit the wider social context of the home setting.
In the local network, home guests can inject their configuration in the local
network policy and improve their experience. This approach is not limited in
the local network and can expand to wider contexts. For example, neighbours can
negotiate  resource control by taking advantage of the social context in a
neighbourhood. Users can coordinate socially to share unutilized resources on
the last mile of the residential connection,  e.g.~exchange high priority
traffic for specific timeslots with neighbours.

Secondly, a number of pieces of work arise from Chapter~\ref{sec:signpost}.  The
\signpost design at the moment is limited in its policy expressiveness, which
though is sufficient to address our motivations.  Nonetheless, the
authentication primitives can provide a scalable and global mechanism to develop
novel network policy frameworks and address a series of problems stemming from
the inability of the network layer to authenticate network end-points.
Furthermore, the hierarchical structure of the \signpost architecture can be
used to reflect higher level social relationship and increase the in-network
flexibility. Bigraph theory provides a sufficient framework to model and scale
the complexity of such control designs. 

% For example, the devices of a user who is a member of the University
% of Cambridge can connect through the \signpost architecture with the university
% network control plane,  when a device is connected to the university network. 
% At run-time the device \signpost daemon can negotiate with the university
% \signpost controller the device network requirements and reflect them in the
% University network control.

\section{Conclusion}

In summary, this dissertation has argued that network technologies exhibit
significant limitation to scale their functionality and support the multiple
aspects of network performance. We identified these limitations on the
unforeseen functional requirements occurring  by the wide adoption of network
technologies. In order to address these limitations, we content that network
control must be redesign and specialized in order to fit the requirements and
the take advantage the properties of the deployment environment. This
dissertation has presented and evaluated mechanisms to control plane
functionality, management and connectivity scalability. 



